%%
%%  Department of Electrical, Electronic and Computer Engineering.
%%  EPR400/2 Final Report - Preamble.
%%  Copyright (C) 2011-2021 University of Pretoria.
%%
This report was compiled to outline the research and production process of developing a non-intrusive load detection energy meter for appliance identification (this device being my final year project submission).
\\[2ex]
\textit{Project proposal and technical documentation} \newline
This main report contains an unaltered copy of the approved Project Proposal (as Part 2 of the report).

Technical documentation appears in Part 4 (Appendix).

All the code that I developed appears as a separate submission on the AMS.
\\[2ex]
\textit{Project history} \newline
The work of Gouhua \emph{et al} in \cite{RN39} was used as a basis and point of departure for this project. However, though the method of identification used is the same as that of Gouha \emph{et al}, the implementation of their work in the creation of the device appears to be unprecedented and original. This project makes extensive use of existing algorithms on decision trees - many of which were adapted from \cite{jauregui_2022}, though other authors' work was also relied upon (and appropriately cited).
\\[2ex]
I reused FFT code from a library and did not develop this myself.
\\
The FIR-Filter design (Type,Window,Order) is my own. I reused the FIR implementation code from a library and did not develop this myself.
\\
I reused HTML framework code from a library and did not develop this myself.  
\\
The rest of the work reported on here, is entirely my own.
\\[2ex]
\textit{Language editing} \newline
This document was edited by a qualified language editor and writing guide. By submitting this document in its present form, I declare that this is the written material that I wish to be examined on.

My language editor was \makebox[3in]{\hrulefill}.

\vspace*{0.5cm}

\begin{tabular}{lp{1cm}ll}
\makebox[3in]{\hrulefill}  &  & \makebox[1.5in]{\hrulefill} \\
\textit{Language editor signature}  &  & \textit{Date}
\end{tabular}

\vspace*{0.5cm}
\newpage
\textit{Declaration}
\\[2ex]
I, \makebox[3in]{\hrulefill} understand what plagiarism is and have carefully studied the plagiarism policy of the University. I hereby declare that all the work described in this report is my own, except where explicitly indicated otherwise. Although I may have discussed the design and investigation with my study leader, fellow students or consulted various books, articles or the internet, the design/investigative work is my own. I have mastered the design and I have made all the required calculations in my lab book (and/or they are reflected in this report) to authenticate this. I am not presenting a complete solution of someone else.

Wherever I have used information from other sources, I have given credit by proper and complete referencing of the source material so that it can be clearly discerned what is my own work and what was quoted from other sources. I acknowledge that failure to comply with the instructions regarding referencing will be regarded as plagiarism.  If there is any doubt about the authenticity of my work, I am willing to attend an oral ancillary examination/evaluation about the work.

I certify that the Project Proposal appearing as the Introduction section of the report is a verbatim copy of the approved Project Proposal.

\begin{tabular}{lp{1cm}ll}
\makebox[3in]{\hrulefill}  &  & \makebox[1.5in]{\hrulefill} \\
\eprthecandidatename       &  & Date
\end{tabular}

%% End of File.

